### 2018-04-23 manuscript.Rnw
revert line numbers and remove todos
author names formated like in plos
oops spelling mistake in marcus' name

\reversemarginpar
\usepackage[colorinlistoftodos]{todonotes}
%\usepackage[colorinlistoftodos,disable]{todonotes}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Rethomics: an R framework to analyse high-throughput behavioural data} 
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Quentin Geissmann\textsuperscript{1*},
Luis G Rodriguez\textsuperscript{2},
Esteban J Beckwith\textsuperscript{1},
Giorgio F Gilestro\textsuperscript{1*}
\\
\bigskip
\textbf{1} Department of Life Sciences, Imperial College London, London, United Kingdom
\\
\textbf{2} Institute for Neuro- and Behavioral Biology, Westf{\"a}lische Wilhelms University, 48149 M{\"u}nster, Germany
\\
\bigskip

@@

\section*{Acknowledgements}
We would like to thank people who have directly or indirectly contributed to the this manuscript.
In particular, Han Kim, for his invaluable comments on the early versions of \texttt{rethomics} and his dedicated contribution to the tutorials;
Maite Ogueta and Ralf Stanewsky, for making the DAMS results data available;
Alice French, Hannah Jones, Diana Bicazan and Florencia Fernandez-Chiappe for their comments as early users;
Marcus Gosh and Tara Kane for their feedback on the manuscript;
Brenna Williams, for her help to support multi-beam DAMS;
Patrick Kr{\"a}tschmer, for his time discussing the conceptual framework.

>>>>

\reversemarginpar
%\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorinlistoftodos,disable]{todonotes}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Rethomics: an R framework to analyse high-throughput behavioural data} 
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Quentin Geissmann\textsuperscript{1*},
Luis Garcia Rodriguez\textsuperscript{2},
Esteban J. Beckwith\textsuperscript{1},
Giorgio F. Gilestro\textsuperscript{1*}
\\
\bigskip
\textbf{1} Department of Life Sciences, Imperial College London, London, United Kingdom
\\
\textbf{2} Institute for Neuro- and Behavioral Biology, Westf{\"a}lische Wilhelms University, 48149 M{\"u}nster, Germany
\\
\bigskip

@@

\section*{Acknowledgements}
We would like to thank people who have directly or indirectly contributed to the this manuscript.
In particular, Han Kim, for his invaluable comments on the early versions of \texttt{rethomics} and his dedicated contribution to the tutorials;
Maite Ogueta and Ralf Stanewsky, for making the DAMS results data available;
Alice French, Hannah Jones, Diana Bicazan and Florencia Fernandez-Chiappe for their comments as early users;
Marcus Ghosh and Tara Kane for their feedback on the manuscript;
Brenna Williams, for her help to support multi-beam DAMS;
Patrick Kr{\"a}tschmer, for his time discussing the conceptual framework.
